Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper.tex
checklist at end removed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@862 d8b0c59b-6544-0410-94d9-83a5658a058e
changed short title
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@869 d8b0c59b-6544-0410-94d9-83a5658a058e

% a short form should be given in case it is too long for the running head
\titlerunning{Web Service Wrapping, Discovery and Consumption --- More Power to the End-User}

@@

\section*{Checklist of Items to be Sent to Volume Editors}
Here is a checklist of everything the volume editor requires from you:

\begin{itemize}
\settowidth{\leftmargin}{{\Large$\square$}}\advance\leftmargin\labelsep
\itemsep8pt\relax
\renewcommand\labelitemi{{\lower1.5pt\hbox{\Large$\square$}}}

\item The final \LaTeX{} source files
\item A final PDF file
\item A copyright form, signed by one author on behalf of all of the
authors of the paper.
\item A readme giving the name and email address of the
corresponding author.
\end{itemize}
\end{document}

>>>>

% a short form should be given in case it is too long for the running head
\titlerunning{Web Service Wrapping, Discovery and Consumption}

@@

% \section*{Checklist of Items to be Sent to Volume Editors}
% Here is a checklist of everything the volume editor requires from you:
% 
% 
% \begin{itemize}
% \settowidth{\leftmargin}{{\Large$\square$}}\advance\leftmargin\labelsep
% \itemsep8pt\relax
% \renewcommand\labelitemi{{\lower1.5pt\hbox{\Large$\square$}}}
% 
% \item The final \LaTeX{} source files
% \item A final PDF file
% \item A copyright form, signed by one author on behalf of all of the
% authors of the paper.
% \item A readme giving the name and email address of the
% corresponding author.
% \end{itemize}
\end{document}
